---
title: "R Notebook"
output: html_notebook
---
```{r}
here::i_am("R/004_Votes_share.vs.nightlight.Rmd")
require(lmtest)
require(plm)
require(stargazer)

#### FUNCTIONS ####
source(here::here("R/function.library.R"))
#### LOAD THE DATA ####

load(here::here("results/data.RData"))

```


# 1. PERCENT-VOTES VS. NIGHLIGHTS


```{r}

share <- data %>% select(index,label,starts_with("kabila.percent"),starts_with("ramazani.percent")) %>%
  pivot_longer(cols = -c(index,label),values_to = "votes_share") %>% separate(name,c("drop","year"),sep="_") %>% mutate(year=as.integer(year)) %>% select(-drop)


share
```

```{r}

share  %>% ggplot() + geom_histogram(aes(x=votes_share,y=(..count..)/sum(..count..)),bins = 1+3.322*log10(nrow(share)/3),color="black",fill="red") + facet_wrap(~year,ncol=3)

```



```{r,include=FALSE}

# Compute neighborhood matrix (used later in diagnostic tests)
library(spdep)

x <- share %>% left_join(congo.territoire.borders,by=c(index="index.data")) %>% filter(year==2006)



nb <- spdep::poly2nb(pl=x$geometry,row.names = x$index)
nbw <- spdep::nb2listw(nb,zero.policy = TRUE,style="B")

nb.matrix <- nb2mat(nb,zero.policy = TRUE,style="B")

summary(nb)

```


## 1.1. mean_nightlight_gt30_with_VIIRS correction

### Data

```{r}


elections <- list("2006"=c(2001:2006),
                  "2011"=c(2007:2011)
                  ) %>% 
  map2(names(.),~rep(.y,length(.x)) %>% 
         set_names(.x)) %>% 
  reduce(c)




mean_nightlight <- nightlight_gt30_mean %>% mutate(nightlight_mean=nightlight_mean+0.01) %>% select(index=index.data,year,nightlight_mean) %>% 
  mutate(election=elections[as.character(year)]) %>%  group_by(index,election) %>% summarise(across(nightlight_mean,~mean(.,na.rm = TRUE)),.groups = "drop") %>% filter(!is.na(election))


DMSP_2012_13 <- nightlight_gt30_mean %>% mutate(nightlight_mean=nightlight_mean+0.01) %>% select(index=index.data,year,nightlight_mean) %>% filter(year %in% c(2012,2013)) %>% group_by(index) %>% summarise(across(nightlight_mean,~mean(.,na.rm = TRUE)),.groups = "drop") 

VIIR_percent_change <- nightlight_gt30_mean %>% mutate(nightlight_mean=nightlight_mean+0.01) %>% select(index=index.data,year,nightlight_mean) %>% filter(year %in% c(2014,2018)) %>% pivot_wider(names_from = year,values_from = nightlight_mean) %>% mutate(change=(`2018`-`2014`)/(`2014`))

VIIR_corrected <- DMSP_2012_13 %>% left_join(VIIR_percent_change,by="index") %>% mutate(nightlight_mean_corrected=nightlight_mean+(nightlight_mean)*change) %>% select(index,nightlight_mean=nightlight_mean_corrected) %>% mutate(election="2018")

mean_nightlight %<>% bind_rows(VIIR_corrected) %>% mutate(year=as.integer(election)) %>% select(-election)

to.model <- share %>% left_join(mean_nightlight,by=c("index","year"))  %>% rename(region=label) %>% select(-index)

# Changes in nightlight

differences <- to.model  %>% select(region,year,nightlight_mean) %>% as.data.frame()  %>% pivot_wider(names_from = "year",values_from = "nightlight_mean") %>%
  mutate(`2006-2011`=`2011`-`2006`,`2011-2018`=`2018`-`2011`) %>% select(-c(`2006`,`2011`,`2018`)) %>% pivot_longer(cols = -region,names_to = "period",values_to = "difference")

g <- ggplot(differences,aes(x=difference)) +geom_histogram(bins = 1+3.322*log10(nrow(to.model)),color="black",fill="red") +
  facet_wrap(~period,ncol=2) + xlab("Change in mean nightlight") + scale_y_continuous(trans="log10") +  ylab("log10(count)")

ggsave(here::here("figures/Mean_nightlight_gt30_diff_histograms.png"),g,width = 5,height = 3)


# plm data format

to.model <- plm::pdata.frame(to.model,index=c("region","year"),drop.index = FALSE)

to.model



```


```{r}

to.model %>% as.data.frame()  %>% ggplot() + geom_histogram(aes(x=nightlight_mean,y=(..count..)/sum(..count..)),bins = 1+3.322*log10(nrow(to.model)/3),color="black",fill="red") + facet_wrap(~year,ncol=3)

```

```{r}
to.model
```


### Model

```{r}
m <- model_1_1 <- plm(votes_share ~ nightlight_mean,data=to.model,model="within",effect = "twoways")

summary(m)

```

Coefficients with robust SE

```{r}

coeftest(m, vcovHC(m, method="arellano", type="HC3"))

```


### Model diagnostics

Cross-sectional dependence test

```{r}

pcdtest(votes_share ~nightlight_mean,data=to.model,model = "within",effect="twoways",w=nb.matrix)

```

Serial correlation test for short panels

```{r}

plm::pwartest(votes_share ~nightlight_mean,data=to.model)

```

Fixed effects test

```{r}
mpool <- plm(votes_share ~nightlight_mean,data=to.model,model="pooling")

plm::pFtest(m,mpool)

```

 Residuals Normality

```{r}
resid <- residuals(m)

qqnorm(resid)
qqline(resid)

```

```{r}

ks.test(resid,"pnorm",mean(resid),sd(resid))

```

```{r}
pred <- predict(m)

plot(as.vector(pred),as.vector(resid),ylab="Residuals",xlab="Fitted")
```




## 1.2. mean_nightlight_gt30_with_VIIRS no correction

### Data

```{r}


elections <- list("2006"=c(2001:2006),
                  "2011"=c(2007:2011),
                  "2018"=c(2014:2018)
                  ) %>% 
  map2(names(.),~rep(.y,length(.x)) %>% 
         set_names(.x)) %>% 
  reduce(c)




mean_nightlight <- nightlight_gt30_mean %>% mutate(nightlight_mean=nightlight_mean+0.01) %>% select(index=index.data,year,nightlight_mean) %>% 
  mutate(election=elections[as.character(year)]) %>%  group_by(index,election) %>% summarise(across(nightlight_mean,~mean(.,na.rm = TRUE)),.groups = "drop") %>% filter(!is.na(election))



mean_nightlight %<>% mutate(year=as.integer(election)) %>% select(-election)

to.model <- share %>% left_join(mean_nightlight,by=c("index","year"))  %>% rename(region=label) %>% select(-index)

to.model <- plm::pdata.frame(to.model,index=c("region","year"),drop.index = FALSE)

to.model



```


```{r}

to.model %>% as.data.frame()  %>% ggplot() + geom_histogram(aes(x=nightlight_mean,y=(..count..)/sum(..count..)),bins = 1+3.322*log10(nrow(to.model)/3),color="black",fill="red") + facet_wrap(~year,ncol=3)

```

### Model

```{r}
m <- model_1_2 <-  plm(votes_share ~ nightlight_mean,data=to.model,model="within",effect = "twoways")

summary(m)

```

Coefficients with robust SE

```{r}

coeftest(m, vcovHC(m, method="arellano", type="HC3"))

```


### Model diagnostics

Cross-sectional dependence test

```{r}

pcdtest(votes_share ~nightlight_mean,data=to.model,model = "within",effect="twoways",w=nb.matrix)

```

Serial correlation test for short panels

```{r}

plm::pwartest(votes_share ~nightlight_mean,data=to.model)

```

Fixed effects test

```{r}
mpool <- plm(votes_share ~nightlight_mean,data=to.model,model="pooling")

plm::pFtest(m,mpool)

```

 Residuals Normality

```{r}
resid <- residuals(m)

qqnorm(resid)
qqline(resid)

```

```{r}

ks.test(resid,"pnorm",mean(resid),sd(resid))

```

```{r}
pred <- predict(m)

plot(as.vector(pred),as.vector(resid),ylab="Residuals",xlab="Fitted")
```

## 1.3. mean_nightlight_with_VIIRS correction

### Data

```{r}


elections <- list("2006"=c(2001:2006),
                  "2011"=c(2007:2011)
                  ) %>% 
  map2(names(.),~rep(.y,length(.x)) %>% 
         set_names(.x)) %>% 
  reduce(c)




mean_nightlight <- nightlight_mean %>% mutate(nightlight_mean=nightlight_mean+0.01) %>% select(index=index.data,year,nightlight_mean) %>% 
  mutate(election=elections[as.character(year)]) %>%  group_by(index,election) %>% summarise(across(nightlight_mean,~mean(.,na.rm = TRUE)),.groups = "drop") %>% filter(!is.na(election))


DMSP_2012_13 <- nightlight_mean %>% mutate(nightlight_mean=nightlight_mean+0.01) %>% select(index=index.data,year,nightlight_mean) %>% filter(year %in% c(2012,2013)) %>% group_by(index) %>% summarise(across(nightlight_mean,~mean(.,na.rm = TRUE)),.groups = "drop") 

VIIR_percent_change <- nightlight_mean %>% mutate(nightlight_mean=nightlight_mean+0.01) %>% select(index=index.data,year,nightlight_mean) %>% filter(year %in% c(2014,2018)) %>% pivot_wider(names_from = year,values_from = nightlight_mean) %>% mutate(change=(`2018`-`2014`)/(`2014`))

VIIR_corrected <- DMSP_2012_13 %>% left_join(VIIR_percent_change,by="index") %>% mutate(nightlight_mean_corrected=nightlight_mean+(nightlight_mean)*change) %>% select(index,nightlight_mean=nightlight_mean_corrected) %>% mutate(election="2018")

mean_nightlight %<>% bind_rows(VIIR_corrected) %>% mutate(year=as.integer(election)) %>% select(-election)

to.model <- share %>% left_join(mean_nightlight,by=c("index","year"))  %>% rename(region=label) %>% select(-index)

# Changes in nightlight

differences <- to.model  %>% select(region,year,nightlight_mean) %>% as.data.frame()  %>% pivot_wider(names_from = "year",values_from = "nightlight_mean") %>%
  mutate(`2006-2011`=`2011`-`2006`,`2011-2018`=`2018`-`2011`) %>% select(-c(`2006`,`2011`,`2018`)) %>% pivot_longer(cols = -region,names_to = "period",values_to = "difference")

g <- ggplot(differences,aes(x=difference)) +geom_histogram(bins = 1+3.322*log10(nrow(to.model)),color="black",fill="red") +
  facet_wrap(~period,ncol=2) + xlab("Change in mean nightlight") + scale_y_continuous(trans="log10") +  ylab("log10(count)")

ggsave(here::here("figures/Mean_nightlight_diff_histograms.png"),g,width = 5,height = 3)


# plm data format

to.model <- plm::pdata.frame(to.model,index=c("region","year"),drop.index = FALSE)

to.model



```


```{r}

to.model %>% as.data.frame()  %>% ggplot() + geom_histogram(aes(x=nightlight_mean,y=(..count..)/sum(..count..)),bins = 1+3.322*log10(nrow(to.model)/3),color="black",fill="red") + facet_wrap(~year,ncol=3)

```

```{r}
to.model
```


### Model

```{r}
m <-  model_1_3 <-  plm(votes_share ~ nightlight_mean,data=to.model,model="within",effect = "twoways")

summary(m)

```

Coefficients with robust SE

```{r}

coeftest(m, vcovHC(m, method="arellano", type="HC3"))

```


### Model diagnostics

Cross-sectional dependence test

```{r}

pcdtest(votes_share ~nightlight_mean,data=to.model,model = "within",effect="twoways",w=nb.matrix)

```

Serial correlation test for short panels

```{r}

plm::pwartest(votes_share ~nightlight_mean,data=to.model)

```

Fixed effects test

```{r}
mpool <- plm(votes_share ~nightlight_mean,data=to.model,model="pooling")

plm::pFtest(m,mpool)

```

 Residuals Normality

```{r}
resid <- residuals(m)

qqnorm(resid)
qqline(resid)

```

```{r}

ks.test(resid,"pnorm",mean(resid),sd(resid))

```

```{r}
pred <- predict(m)

plot(as.vector(pred),as.vector(resid),ylab="Residuals",xlab="Fitted")
```

```{r,results='asis'}

models.to.print <- list(model_1_1,model_1_2,model_1_3)

model_names <- c("Corrected GT30","Not Corrected GT30","Corrected All")

models.to.print_se <- map(models.to.print,~coeftest(.x, vcovHC(.x, method="arellano", type="HC3"))[,"Std. Error"])

out.file <- here::here("tables/votes_share.vs.nightlight_models.html")

 F.stat <-map(models.to.print,~{
  summ <- summary(.x,vcov.=vcovHC(.x, method="arellano", type="HC3"))
  
  .p <- summ$fstatistic$p.value
  sprintf("%0.3f%s",summ$fstatistic$statistic,
  case_when(.p<0.01 ~"***",
            .p<0.05 ~"**",
            .p<0.1~"*",
            TRUE ~""))
  
  
})  %>% unlist %>% c("F Statistic",.)

  df <-map(models.to.print,~{
  summ <- summary(.x,vcov.=vcovHC(.x, method="arellano", type="HC3"))
  
  paste(summ$fstatistic$parameter,collapse=";")
  
  
})  %>% unlist %>% c("df",.)
 

suppressWarnings(stargazer::stargazer(models.to.print,type="html",
                                      se=models.to.print_se,
                                      out =out.file ,
                                      column.labels=model_names,dep.var.caption = "Votes share",
                                      omit.stat = "f",
                                      add.lines = list(F.stat,
                                                       df)))

```


