---
title: "TURNOUT VS. CONFLICTS + NIGHTLIGHT"
output: 
  html_notebook:
    theme: united
    toc: yes
---
```{r}
here::i_am("R/005_Turnout.vs.conflicts_nightlight.Rmd")
require(lmtest)
require(plm)
require(stargazer)

#### FUNCTIONS ####
source(here::here("R/function.library.R"))
#### LOAD THE DATA ####

load(here::here("results/data.RData"))

```


# 1. EXPLORATORY

## 1.1 Turnout data

```{r}

turnout <- data %>% select(index,label,starts_with("turnout_")) %>%
  pivot_longer(cols = -c(index,label),values_to = "turnout") %>% separate(name,c("drop","year"),sep="_") %>% mutate(year=as.integer(year)) %>% select(-drop)


turnout
```

```{r}

turnout  %>% ggplot() + geom_histogram(aes(x=turnout,y=(..count..)/sum(..count..)),bins = 1+3.322*log10(nrow(turnout)/3),color="black",fill="red") + facet_wrap(~year,ncol=3)

```
```{r}

turnout  %>% ggplot() + geom_histogram(aes(x=turnout),bins = 1+3.322*log10(nrow(turnout)/3),color="black",fill="red") + facet_wrap(~year,ncol=3)

```


```{r,include=FALSE}

# Compute neighborhood matrix (used later in diagnostic tests)
library(spdep)

x <- turnout %>% left_join(congo.territoire.borders,by=c(index="index.data")) %>% filter(year==2006)



nb <- spdep::poly2nb(pl=x$geometry,row.names = x$index)
nbw <- spdep::nb2listw(nb,zero.policy = TRUE,style="B")

nb.matrix <- nb2mat(nb,zero.policy = TRUE,style="B")

summary(nb)

```


<a href="#top">Back to top</a>

## 1.2 Nightlight data


```{r}
elections <- list("2006"=c(2001:2006),
                  "2011"=c(2007:2011)
                  ) %>% 
  map2(names(.),~rep(.y,length(.x)) %>% 
         set_names(.x)) %>% 
  reduce(c)




mean_nightlight <- nightlight_gt30_mean %>% mutate(nightlight_mean=nightlight_mean+0.01) %>% select(index=index.data,year,nightlight_mean) %>% 
  mutate(election=elections[as.character(year)]) %>%  group_by(index,election) %>% summarise(across(nightlight_mean,~mean(.,na.rm = TRUE)),.groups = "drop") %>% filter(!is.na(election))


DMSP_2012_13 <- nightlight_gt30_mean %>% mutate(nightlight_mean=nightlight_mean+0.01) %>% select(index=index.data,year,nightlight_mean) %>% filter(year %in% c(2012,2013)) %>% group_by(index) %>% summarise(across(nightlight_mean,~mean(.,na.rm = TRUE)),.groups = "drop") 

VIIR_percent_change <- nightlight_gt30_mean %>% mutate(nightlight_mean=nightlight_mean+0.01) %>% select(index=index.data,year,nightlight_mean) %>% filter(year %in% c(2014,2018)) %>% pivot_wider(names_from = year,values_from = nightlight_mean) %>% mutate(change=(`2018`-`2014`)/(`2014`))

VIIR_corrected <- DMSP_2012_13 %>% left_join(VIIR_percent_change,by="index") %>% mutate(nightlight_mean_corrected=nightlight_mean+(nightlight_mean)*change) %>% select(index,nightlight_mean=nightlight_mean_corrected) %>% mutate(election="2018")

mean_nightlight %<>% bind_rows(VIIR_corrected) %>% mutate(year=as.integer(election)) %>% select(-election)

turnout %<>% left_join(mean_nightlight,by=c("index","year"))
```

```{r}

turnout %>% as.data.frame()  %>% ggplot() + geom_histogram(aes(x=nightlight_mean,y=(..count..)/sum(..count..)),bins = 1+3.322*log10(nrow(turnout)/3),color="black",fill="red") + facet_wrap(~year,ncol=3)

```

<a href="#top">Back to top</a>

## 1.3 Conflict & deaths data


```{r,include=TRUE}

total_conflict_deaths <- conflict.aggregated_by_type %>% select(index=index.data,year,n.deaths) %>% group_by(index,year) %>% summarise(across(n.deaths,~sum(.,na.rm = TRUE)),.groups = "drop")


total_conflict_deaths <- turnout %>% select(-turnout) %>% left_join(total_conflict_deaths,by=c("index","year")) %>% mutate(n.deaths=replace_na(n.deaths,0)) %>% rename(region=label) %>% select(-index)


to.plot <- total_conflict_deaths %>% group_by(year) %>% summarise(`units with n.deaths >0`=sum(n.deaths>0),`units with 0 deaths`=sum(n.deaths==0),.groups = "drop") %>% mutate(year=as.character(year))

to.plot %<>% bind_rows(to.plot %>% summarise(year="Total",across(where(is.numeric),sum)))

to.plot

```
```{r,include=TRUE}

to.test <- total_conflict_deaths %>% group_by(year) %>% summarise(any_deaths=sum(n.deaths>0),no_deaths=sum(n.deaths==0)) %>% select(-year) %>% as.matrix()

chisq.test(to.test,correct = T)


```


```{r,include=TRUE}

total_conflict_events <- conflict.aggregated_by_type %>% select(index=index.data,year,n.conflicts) %>% group_by(index,year) %>% summarise(across(n.conflicts,~sum(.,na.rm = TRUE)),.groups = "drop")


total_conflict_events <- turnout %>% select(-turnout) %>% left_join(total_conflict_events,by=c("index","year")) %>% mutate(n.conflicts=replace_na(n.conflicts,0)) %>% rename(region=label) %>% select(-index)


to.plot <- total_conflict_events %>% group_by(year) %>% summarise(`units with n.conflicts >0`=sum(n.conflicts>0),`units with 0 conflicts`=sum(n.conflicts==0),.groups = "drop") %>% mutate(year=as.character(year))

to.plot %<>% bind_rows(to.plot %>% summarise(year="Total",across(where(is.numeric),sum)))

to.plot


```
```{r,include=TRUE}

to.test <- total_conflict_events %>% group_by(year) %>% summarise(any_conflicts=sum(n.conflicts>0),no_conflicts=sum(n.conflicts==0)) %>% select(-year) %>% as.matrix()

chisq.test(to.test,correct = T)


```


<a href="#top">Back to top</a>

# 2. MODELS

## 2.1. total_conflict_deaths

### Data

```{r}
total_conflict_deaths <- conflict.aggregated_by_type %>% select(index=index.data,year,n.deaths) %>% group_by(index,year) %>% summarise(across(n.deaths,~sum(.,na.rm = TRUE)),.groups = "drop")


to.model <- turnout %>% left_join(total_conflict_deaths,by=c("index","year")) %>% mutate(n.deaths=replace_na(n.deaths,0)) %>% rename(region=label) %>% select(-index)

to.model <- plm::pdata.frame(to.model,index=c("region","year"),drop.index = FALSE)

to.model



```


```{r}

to.model %>% as.data.frame()  %>% ggplot() + geom_histogram(aes(x=n.deaths,y=(..count..)/sum(..count..)),bins = 1+3.322*log10(nrow(to.model)/3),color="black",fill="red") + facet_wrap(~year,ncol=3)

```

```{r}

to.model %>% as.data.frame()  %>% ggplot() + geom_histogram(aes(x=n.deaths),bins = 1+3.322*log10(nrow(to.model)/3),color="black",fill="red") + facet_wrap(~year,ncol=3)

```

```{r}

to.model %>% as.data.frame() %>% filter(n.deaths >0) %>% ggplot() + geom_histogram(aes(x=n.deaths),bins = 1+3.322*log10(nrow(to.model %>% filter(n.deaths >0))/3),color="black",fill="red") + facet_wrap(~year,ncol=3) + ggtitle("# deaths >0")

```

<a href="#top">Back to top</a>

### Change

```{r}
.to_plot <- to.model %>% as.data.frame() %>% select(-turnout) %>% pivot_wider(id_cols = region,names_from = "year",values_from = "n.deaths") %>%
  mutate(change_2006_2011=`2011`-`2006`,
         change_2011_2018=`2018`-`2011`) %>%
  select(region,starts_with("change_"))
.to_plot
```

```{r}
.to_plot %<>%
  pivot_longer(cols=-region,values_to = "change")
  

.to_plot %>%  ggplot() + geom_histogram(aes(x=change,y=log10(..count..)),
                                        bins = 1+3.322*log10(nrow(.to_plot)/2),
                                        color="black",fill="red") + facet_wrap(~name,ncol=2)

```

```{r}

  

.to_plot %>%  ggplot() + geom_histogram(aes(x=sign(change)*log10(abs(change)+1),y=log10(..count..)),
                                        bins = 1+3.322*log10(nrow(.to_plot)/2),
                                        color="black",fill="red") + facet_wrap(~name,ncol=2)

```

<a href="#top">Back to top</a>


### Model

```{r}
m <- model1_1 <- plm(turnout ~ nightlight_mean +n.deaths,data=to.model,model="within",effect = "twoways")

summary(m)

```

Coefficients with robust SE

```{r}

coeftest(m, vcovHC(m, method="arellano", type="HC3"))

```

<a href="#top">Back to top</a>



### Model diagnostics

Cross-sectional dependence test

```{r}

pcdtest(turnout ~ nightlight_mean +n.deaths,data=to.model,model = "within",effect="twoways",w=nb.matrix)

```

Serial correlation test for short panels

```{r}

plm::pwartest(turnout ~ nightlight_mean +n.deaths,data=to.model)

```

Fixed effects test

```{r}
mpool <- plm::plm(turnout ~ nightlight_mean +n.deaths,data=to.model,model="pooling")

plm::pFtest(m,mpool)

```

 Residuals Normality

```{r}
resid <- residuals(m)

qqnorm(resid)
qqline(resid)

```

```{r}

ks.test(resid,"pnorm",mean(resid),sd(resid))

```

```{r}
pred <- predict(m)

plot(as.vector(pred),as.vector(resid),ylab="Residuals",xlab="Fitted")
```

<a href="#top">Back to top</a>



## 2.2. log_total_conflict_deaths

### Data

```{r}

log_total_conflict_deaths <- conflict.aggregated_by_type %>% select(index=index.data,year,n.deaths) %>% group_by(index,year) %>% summarise(across(n.deaths,~log(sum(.,na.rm = TRUE)+0.1)),.groups = "drop") %>% rename(log_n.deaths=n.deaths)


to.model <- turnout %>% left_join(log_total_conflict_deaths,by=c("index","year")) %>% mutate(log_n.deaths=replace_na(log_n.deaths,0)) %>% rename(region=label) %>% select(-index)

to.model <- plm::pdata.frame(to.model,index=c("region","year"),drop.index = FALSE)

to.model

```

```{r}

to.model %>% as.data.frame()  %>% ggplot() + geom_histogram(aes(x=log_n.deaths,y=(..count..)/sum(..count..)),bins = 1+3.322*log10(nrow(to.model)/3),color="black",fill="red") + facet_wrap(~year,ncol=3)

```


```{r}

to.model %>% as.data.frame()  %>% ggplot() + geom_histogram(aes(x=log_n.deaths),bins = 1+3.322*log10(nrow(to.model)/3),color="black",fill="red") + facet_wrap(~year,ncol=3)

```

<a href="#top">Back to top</a>

### Model

```{r}

m <- model1_2 <- plm(turnout ~ nightlight_mean +log_n.deaths,data=to.model,model="within",effect = "twoways")

summary(m)
```

Coefficients with robust SE

```{r}

coeftest(m, vcovHC(m, method="arellano", type="HC3"))

```


<a href="#top">Back to top</a>

### Model diagnostics

Cross-sectional dependence test


```{r}

pcdtest(turnout ~ nightlight_mean +log_n.deaths,data=to.model,model = "within",effect="twoways",w=nb.matrix)

```

Serial correlation test for short panels

```{r}

plm::pwartest(turnout ~ nightlight_mean +log_n.deaths,data=to.model)

```

Fixed effects test

```{r}
mpool <- plm::plm(turnout ~ nightlight_mean +log_n.deaths,data=to.model,model="pooling")

plm::pFtest(m,mpool)

```

Residuals Normality

```{r}
resid <- residuals(m)

qqnorm(resid)
qqline(resid)

```

```{r}

ks.test(resid,"pnorm",mean(resid),sd(resid))

```

```{r}
pred <- predict(m)

plot(as.vector(pred),as.vector(resid),ylab="Residuals",xlab="Fitted")
```




<a href="#top">Back to top</a>

## 2.3. conflict_deaths_by_type

### Data

```{r}

conflict_deaths_by_type <- conflict.aggregated_by_type %>% select(index=index.data,year,type,n.deaths) %>% mutate(type=paste0(type,"_deaths")) %>% pivot_wider(names_from = type,values_from = n.deaths)


to.model <- turnout %>% left_join(conflict_deaths_by_type,by=c("index","year")) %>% mutate(across(-c(index,year,turnout),~replace_na(.,0))) %>% rename(region=label) %>% select(-index)

to.model <- plm::pdata.frame(to.model,index=c("region","year"),drop.index = FALSE)


to.model

```


```{r,fig.width=10}

to.model %>% as.data.frame() %>% pivot_longer(cols=-c(region,year,turnout))  %>% ggplot() + geom_histogram(aes(x=value,y=(..count..)/sum(..count..)),bins = 1+3.322*log10(nrow(to.model)/3),color="black",fill="red") + facet_grid(year~name)

```
```{r,fig.width=10}

to.model %>% as.data.frame() %>% pivot_longer(cols=-c(region,year,turnout))  %>% ggplot() + geom_histogram(aes(x=value),bins = 1+3.322*log10(nrow(to.model)/3),color="black",fill="red") + facet_grid(year~name)

```
```{r,fig.width=10}

to.model %>% as.data.frame() %>% pivot_longer(cols=-c(region,year,turnout))  %>% filter(value >0)  %>% ggplot() + geom_histogram(aes(x=value),bins = 1+3.322*log10(nrow(to.model)/3),color="black",fill="red") + facet_grid(year~name)  + ggtitle("# deaths >0")

```


<a href="#top">Back to top</a>

### Change

```{r}
.to_plot <- to.model %>% as.data.frame() %>% select(-turnout) %>%
  pivot_longer(cols=-c(region,year),names_to = "var",values_to = "value") %>%
  nest(data=-var) %>% mutate(data=map(data,~{
    .x %>% pivot_wider(id_cols = region,names_from = "year",values_from = "value") %>%
  mutate(change_2006_2011=`2011`-`2006`,
         change_2011_2018=`2018`-`2011`) %>%
  select(region,starts_with("change_")) %>% data.frame
  }))

 
.to_plot %>%mutate(data=map(data,~ .x %>%pivot_longer(cols=-c(region),values_to = "change")))%>%  unnest(data) %>% unite(col="var",var,name) %>%
  pivot_wider(names_from = "var",values_from = "change")

```

```{r,fig.width=10}
.to_plot %<>%mutate(data=map(data,~ .x %>%pivot_longer(cols=-c(region),values_to = "change")))%>%  unnest(data)
  

.to_plot %>%  ggplot() + geom_histogram(aes(x=change),bins = 1+3.322*log10(nrow(.to_plot)/2/6),color="black",fill="red") + facet_grid(name~var) 

```

```{r,fig.width=10}

  

.to_plot %>%  ggplot() + geom_histogram(aes(x=sign(change)*log10(abs(change)+1),y=log10(..count..)),bins = 1+3.322*log10(nrow(.to_plot)/2/6),color="black",fill="red") + facet_grid(name~var) 

```



<a href="#top">Back to top</a>

### Model

```{r}

m <- model1_3 <- plm(turnout ~ nightlight_mean +Non.state.vs.non.state_deaths + Foreign.vs.non.state_deaths + Non.state.vs.civilians_deaths + DRC.vs.non.state_deaths + DRC.vs.civilians_deaths +Foreign.vs.civilians_deaths,data=to.model,model="within",effect = "twoways")

summary(m)


```

Coefficients with robust SE

```{r}

coeftest(m, vcovHC(m, method="arellano", type="HC3"))

```


<a href="#top">Back to top</a>

### Model diagnostics

Cross-sectional dependence test


```{r}
pcdtest(turnout ~ nightlight_mean +Non.state.vs.non.state_deaths + Foreign.vs.non.state_deaths + Non.state.vs.civilians_deaths + DRC.vs.non.state_deaths + DRC.vs.civilians_deaths +Foreign.vs.civilians_deaths,data=to.model,model = "within",effect="twoways",w=nb.matrix)
```
Serial correlation test for short panels

```{r}

plm::pwartest(turnout ~ nightlight_mean +Non.state.vs.non.state_deaths + Foreign.vs.non.state_deaths + Non.state.vs.civilians_deaths + DRC.vs.non.state_deaths + DRC.vs.civilians_deaths +Foreign.vs.civilians_deaths,data=to.model)

```

Fixed effects test

```{r}
mpool <- plm::plm(turnout ~ nightlight_mean +Non.state.vs.non.state_deaths + Foreign.vs.non.state_deaths + Non.state.vs.civilians_deaths + DRC.vs.non.state_deaths + DRC.vs.civilians_deaths +Foreign.vs.civilians_deaths,data=to.model,model="pooling")

plm::pFtest(m,mpool)

```

Residuals Normality

```{r}
resid <- residuals(m)

qqnorm(resid)
qqline(resid)

```

```{r}

ks.test(resid,"pnorm",mean(resid),sd(resid))

```

```{r}
pred <- predict(m)

plot(as.vector(pred),as.vector(resid),ylab="Residuals",xlab="Fitted")
```




<a href="#top">Back to top</a>

## 2.4. total_conflict_events

### Data

```{r}

total_conflict_events <- conflict.aggregated_by_type %>% select(index=index.data,year,n.conflicts) %>% group_by(index,year) %>% summarise(across(n.conflicts,~sum(.,na.rm = TRUE)),.groups = "drop")


to.model <- turnout %>% left_join(total_conflict_events,by=c("index","year")) %>% mutate(n.conflicts=replace_na(n.conflicts,0)) %>% rename(region=label) %>% select(-index)

to.model <- plm::pdata.frame(to.model,index=c("region","year"),drop.index = FALSE)


```


```{r}

to.model %>% as.data.frame()  %>% ggplot() + geom_histogram(aes(x=n.conflicts,y=(..count..)/sum(..count..)),bins = 1+3.322*log10(nrow(to.model)/3),color="black",fill="red") + facet_wrap(~year,ncol=3)

```
```{r}

to.model %>% as.data.frame()  %>% ggplot() + geom_histogram(aes(x=n.conflicts),bins = 1+3.322*log10(nrow(to.model)/3),color="black",fill="red") + facet_wrap(~year,ncol=3)

```
```{r}

to.model %>% as.data.frame() %>% filter(n.conflicts >0) %>% ggplot() + geom_histogram(aes(x=n.conflicts),bins = 1+3.322*log10(nrow(to.model%>% filter(n.conflicts >0))/3),color="black",fill="red") + facet_wrap(~year,ncol=3) + ggtitle("# conflicts >0")

```

<a href="#top">Back to top</a>

### Change

```{r}
.to_plot <- to.model %>% as.data.frame() %>% select(-turnout) %>% pivot_wider(id_cols = region,names_from = "year",values_from = "n.conflicts") %>%
  mutate(change_2006_2011=`2011`-`2006`,
         change_2011_2018=`2018`-`2011`) %>%
  select(region,starts_with("change_"))
.to_plot
```

```{r}
.to_plot %<>%
  pivot_longer(cols=-region,values_to = "change")
  

.to_plot %>%  ggplot() + geom_histogram(aes(x=change,y=log10(..count..)),
                                        bins = 1+3.322*log10(nrow(.to_plot)/2),
                                        color="black",fill="red") + facet_wrap(~name,ncol=2)

```

```{r}

  

.to_plot %>%  ggplot() + geom_histogram(aes(x=sign(change)*log10(abs(change)+1),y=log10(..count..)),
                                        bins = 1+3.322*log10(nrow(.to_plot)/2),
                                        color="black",fill="red") + facet_wrap(~name,ncol=2)

```


<a href="#top">Back to top</a>

### Model

```{r}
m <- model1_4 <- plm(turnout ~ nightlight_mean +n.conflicts,data=to.model,model="within",effect = "twoways")

summary(m)


```

Coefficients with robust SE

```{r}

coeftest(m, vcovHC(m, method="arellano", type="HC3"))

```


<a href="#top">Back to top</a>

### Model diagnostics

Cross-sectional dependence test


```{r}
pcdtest(turnout ~ nightlight_mean +n.conflicts,data=to.model,model = "within",effect="twoways",w = nb.matrix)
```

Serial correlation test for short panels

```{r}

plm::pwartest(turnout ~ nightlight_mean +n.conflicts,data=to.model)

```


Fixed effects test

```{r}
mpool <- plm::plm(turnout ~ nightlight_mean +n.conflicts,data=to.model,model="pooling")

plm::pFtest(m,mpool)

```

Residuals Normality

```{r}
resid <- residuals(m)

qqnorm(resid)
qqline(resid)

```

```{r}

ks.test(resid,"pnorm",mean(resid),sd(resid))

```

```{r}
pred <- predict(m)

plot(as.vector(pred),as.vector(resid),ylab="Residuals",xlab="Fitted")
```




<a href="#top">Back to top</a>

## 2.5. log_total_conflict_events

### Data 

```{r}

log_total_conflict_events <- conflict.aggregated_by_type %>% select(index=index.data,year,n.conflicts) %>% group_by(index,year) %>% summarise(across(n.conflicts,~log(sum(.,na.rm = TRUE)+0.1)),.groups = "drop") %>% rename(log_n.conflicts=n.conflicts)


to.model <- turnout %>% left_join(log_total_conflict_events,by=c("index","year")) %>% mutate(log_n.conflicts=replace_na(log_n.conflicts,0)) %>% rename(region=label) %>% select(-index)

to.model <- plm::pdata.frame(to.model,index=c("region","year"),drop.index = FALSE)

to.model 

```
```{r}

to.model %>% as.data.frame()  %>% ggplot() + geom_histogram(aes(x=log_n.conflicts,y=(..count..)/sum(..count..)),bins = 1+3.322*log10(nrow(to.model)/3),color="black",fill="red") + facet_wrap(~year,ncol=3)

```

```{r}

to.model %>% as.data.frame()  %>% ggplot() + geom_histogram(aes(x=log_n.conflicts),bins = 1+3.322*log10(nrow(to.model)/3),color="black",fill="red") + facet_wrap(~year,ncol=3)

```


<a href="#top">Back to top</a>

### Model

```{r}

m <- model1_5 <- plm(turnout ~ nightlight_mean +log_n.conflicts,data=to.model,model="within",effect = "twoways")

summary(m)


```

Coefficients with robust SE

```{r}

coeftest(m, vcovHC(m, method="arellano", type="HC3"))

```


<a href="#top">Back to top</a>

### Model diagnostics

Cross-sectional dependence test


```{r}
pcdtest(turnout ~ nightlight_mean +log_n.conflicts,data=to.model,model = "within",effect="twoways",w=nb.matrix)
```

Serial correlation test for short panels

```{r}

plm::pwartest(turnout ~ nightlight_mean +log_n.conflicts,data=to.model)

```

Fixed effects test

```{r}
mpool <- plm::plm(turnout ~ nightlight_mean +log_n.conflicts,data=to.model,model="pooling")

plm::pFtest(m,mpool)

```

Residuals Normality

```{r}
resid <- residuals(m)

qqnorm(resid)
qqline(resid)

```

```{r}

ks.test(resid,"pnorm",mean(resid),sd(resid))

```

```{r}
pred <- predict(m)

plot(as.vector(pred),as.vector(resid),ylab="Residuals",xlab="Fitted")
```




<a href="#top">Back to top</a>

## 2.6. conflict_events_by_type

### Data

```{r}

conflict_events_by_type <- conflict.aggregated_by_type %>% select(index=index.data,year,type,n.conflicts) %>% mutate(type=paste0(type,"_events")) %>% pivot_wider(names_from = type,values_from = n.conflicts)


to.model <- turnout %>% left_join(conflict_events_by_type,by=c("index","year")) %>% mutate(across(-c(index,year,turnout),~replace_na(.,0))) %>% rename(region=label) %>% select(-index)

to.model <- plm::pdata.frame(to.model,index=c("region","year"),drop.index = FALSE)


to.model
```

```{r,fig.width=10}

to.model %>% as.data.frame() %>% pivot_longer(cols=-c(region,year,turnout))  %>% ggplot() + geom_histogram(aes(x=value,y=(..count..)/sum(..count..)),bins = 1+3.322*log10(nrow(to.model)/3),color="black",fill="red") + facet_grid(year~name)

```

```{r,fig.width=10}

to.model %>% as.data.frame() %>% pivot_longer(cols=-c(region,year,turnout))  %>% ggplot() + geom_histogram(aes(x=value),bins = 1+3.322*log10(nrow(to.model)/3),color="black",fill="red") + facet_grid(year~name)

```

```{r,fig.width=10}

to.model %>% as.data.frame() %>% pivot_longer(cols=-c(region,year,turnout)) %>% filter(value >0)  %>% ggplot() + geom_histogram(aes(x=value),bins = 1+3.322*log10(nrow(to.model)/3),color="black",fill="red") + facet_grid(year~name) + ggtitle("# conflict >0")

```


<a href="#top">Back to top</a>

### Change

```{r}
.to_plot <- to.model %>% as.data.frame() %>% select(-turnout) %>%
  pivot_longer(cols=-c(region,year),names_to = "var",values_to = "value") %>%
  nest(data=-var) %>% mutate(data=map(data,~{
    .x %>% pivot_wider(id_cols = region,names_from = "year",values_from = "value") %>%
  mutate(change_2006_2011=`2011`-`2006`,
         change_2011_2018=`2018`-`2011`) %>%
  select(region,starts_with("change_")) %>% data.frame
  }))

 
.to_plot %>%mutate(data=map(data,~ .x %>%pivot_longer(cols=-c(region),values_to = "change")))%>%  unnest(data) %>% unite(col="var",var,name) %>%
  pivot_wider(names_from = "var",values_from = "change")

```

```{r,fig.width=10}
.to_plot %<>%mutate(data=map(data,~ .x %>%pivot_longer(cols=-c(region),values_to = "change")))%>%  unnest(data)
  

.to_plot %>%  ggplot() + geom_histogram(aes(x=change),bins = 1+3.322*log10(nrow(.to_plot)/2/6),color="black",fill="red") + facet_grid(name~var) 

```

```{r,fig.width=10}

  

.to_plot %>%  ggplot() + geom_histogram(aes(x=sign(change)*log10(abs(change)+1),y=log10(..count..)),bins = 1+3.322*log10(nrow(.to_plot)/2/6),color="black",fill="red") + facet_grid(name~var) 

```



<a href="#top">Back to top</a>

### Model

```{r}

m <- model1_6 <- plm(turnout ~ nightlight_mean +Non.state.vs.non.state_events + Foreign.vs.non.state_events + Non.state.vs.civilians_events + DRC.vs.non.state_events + DRC.vs.civilians_events +Foreign.vs.civilians_events,data=to.model,model="within",effect = "twoways")

summary(m)


```

Coefficients with robust SE

```{r}

coeftest(m, vcovHC(m, method="arellano", type="HC3"))

```


<a href="#top">Back to top</a>

### Model diagnostics

Cross-sectional dependence test




```{r}
pcdtest(turnout ~ nightlight_mean +Non.state.vs.non.state_events + Foreign.vs.non.state_events + Non.state.vs.civilians_events + DRC.vs.non.state_events + DRC.vs.civilians_events +Foreign.vs.civilians_events,data=to.model,model = "within",effect="twoways",w=nb.matrix)
```

Cross-sectional dependence

```{r}

plm::pwartest(turnout ~ nightlight_mean +Non.state.vs.non.state_events + Foreign.vs.non.state_events + Non.state.vs.civilians_events + DRC.vs.non.state_events + DRC.vs.civilians_events +Foreign.vs.civilians_events,data=to.model)

```

Fixed effects test

```{r}
mpool <- plm::plm(turnout ~ nightlight_mean +Non.state.vs.non.state_events + Foreign.vs.non.state_events + Non.state.vs.civilians_events + DRC.vs.non.state_events + DRC.vs.civilians_events +Foreign.vs.civilians_events,data=to.model,model="pooling")

plm::pFtest(m,mpool)

```


Residuals Normality

```{r}
resid <- residuals(m)

qqnorm(resid)
qqline(resid)

```

```{r}

ks.test(resid,"pnorm",mean(resid),sd(resid))

```

```{r}
pred <- predict(m)

plot(as.vector(pred),as.vector(resid),ylab="Residuals",xlab="Fitted")
```





<a href="#top">Back to top</a>

## 2.7. conflict_deaths_by_side

### Data

```{r}


.summarise_var<- function(.x,.var){
  if(!is.null(.x)){
    
    .x %>% as.data.frame() %>%summarise(across(one_of(.var),~sum(.,na.rm = TRUE))) %>% pull(.var)
  }
}

conflict_deaths_by_casualty_type <- conflict.aggregated_by_type %>% mutate(n.deaths_a=map(conflict.data,~.summarise_var(.x,"deaths_a")),
                                       n.deaths_b=map(conflict.data,~.summarise_var(.x,"deaths_b")),
                                       n.deaths_civilians=map(conflict.data,~.summarise_var(.x,"deaths_civilians")),
                                       n.deaths_unknow=map(conflict.data,~.summarise_var(.x,"deaths_unknown"))
                                       ) %>%
  unnest(c(starts_with("n.deaths")))


conflict_deaths_by_casualty_type %<>% mutate(n.deaths_DRC_milit=case_when(str_detect(type,"DRC")~n.deaths_a,TRUE~0),
                                            n.deaths_foreign_milit=case_when(str_detect(type,"Foreign")~n.deaths_a,TRUE~0),
                                            n.deaths_non_state=case_when(type=="Non-state vs non-state"~n.deaths_a+n.deaths_b,
                                                                         type=="Non-state vs civilians"~n.deaths_a,
                                              str_ends(type,"non-state")~n.deaths_b,
                                                                         TRUE~0))



conflict_deaths_by_casualty_type %<>% select(index=index.data,year,n.deaths,n.deaths_DRC_milit,n.deaths_foreign_milit,n.deaths_non_state,n.deaths_civilians,n.deaths_unknow)

conflict_deaths_by_casualty_type %<>% group_by(index,year) %>% summarise(across(everything(),~sum(.,na.rm = FALSE)),.groups="drop")


to.print <- conflict_deaths_by_casualty_type %>% select(-index) %>% group_by(year) %>%  summarise(across(everything(),~sum(.,na.rm = TRUE)),.groups = "drop")

to.print %<>% select(Year=year,`DRC military`=n.deaths_DRC_milit,`Foreign military`=n.deaths_foreign_milit,Civilians=n.deaths_civilians, `Non State`=n.deaths_non_state,Unknown=n.deaths_unknow,Total=n.deaths) %>%
  pivot_longer(cols = -Year,names_to = "Type") %>% pivot_wider(names_from = Year,values_from = value) %>%
  flextable::flextable() %>% flextable::hline(5,border = officer::fp_border()) %>% flextable::autofit()

doc <- read_docx()



doc %<>% body_add_par("Conflict deaths by side",style="table title")
doc %<>% body_add_flextable(to.print,align = "center")


print(doc,target=here::here("tables/Conflict.deaths.by.side.docx"))


to.model <- turnout %>% left_join(conflict_deaths_by_casualty_type,by=c("index","year")) %>% mutate(across(-c(index,year,turnout),~replace_na(.,0))) %>% rename(region=label) %>% select(-index)

to.model <- plm::pdata.frame(to.model,index=c("region","year"),drop.index = FALSE)


to.model
```

```{r,fig.width=10}

to.model  %>% as.data.frame() %>% pivot_longer(cols=-c(region,year,turnout))  %>% ggplot() + geom_histogram(aes(x=value,y=(..count..)/sum(..count..)),bins = 1+3.322*log10(nrow(to.model)/3),color="black",fill="red") + facet_grid(year~name)

```

```{r,fig.width=10}

to.model  %>% as.data.frame() %>% pivot_longer(cols=-c(region,year,turnout))  %>% ggplot() + geom_histogram(aes(x=value),bins = 1+3.322*log10(nrow(to.model)/3),color="black",fill="red") + facet_grid(year~name)

```


```{r,fig.width=10}

to.model  %>% as.data.frame() %>% pivot_longer(cols=-c(region,year,turnout))%>% filter(value>0)  %>% ggplot() + geom_histogram(aes(x=value),bins = 1+3.322*log10(nrow(to.model)/3),color="black",fill="red") + facet_grid(year~name) + ggtitle("# deaths >0")

```


<a href="#top">Back to top</a>

### Change

```{r}
.to_plot <- to.model %>% as.data.frame() %>% select(-turnout) %>%
  pivot_longer(cols=-c(region,year),names_to = "var",values_to = "value") %>%
  nest(data=-var) %>% mutate(data=map(data,~{
    .x %>% pivot_wider(id_cols = region,names_from = "year",values_from = "value") %>%
  mutate(change_2006_2011=`2011`-`2006`,
         change_2011_2018=`2018`-`2011`) %>%
  select(region,starts_with("change_")) %>% data.frame
  }))

 
.to_plot %>%mutate(data=map(data,~ .x %>%pivot_longer(cols=-c(region),values_to = "change")))%>%  unnest(data) %>% unite(col="var",var,name) %>%
  pivot_wider(names_from = "var",values_from = "change")

```

```{r,fig.width=10}
.to_plot %<>%mutate(data=map(data,~ .x %>%pivot_longer(cols=-c(region),values_to = "change")))%>%  unnest(data)
  

.to_plot %>%  ggplot() + geom_histogram(aes(x=change),bins = 1+3.322*log10(nrow(.to_plot)/2/6),color="black",fill="red") + facet_grid(name~var) 

```

```{r,fig.width=10}

  

.to_plot %>%  ggplot() + geom_histogram(aes(x=sign(change)*log10(abs(change)+1),y=log10(..count..)),bins = 1+3.322*log10(nrow(.to_plot)/2/6),color="black",fill="red") + facet_grid(name~var) 

```



<a href="#top">Back to top</a>

### Model

```{r}

m <- model1_7 <- plm(turnout ~ nightlight_mean +n.deaths_DRC_milit + n.deaths_foreign_milit +  n.deaths_non_state + n.deaths_civilians + n.deaths_unknow,data=to.model,model="within",effect = "twoways")

summary(m)


```

Coefficients with robust SE

```{r}

coeftest(m, vcovHC(m, method="arellano", type="HC3"))

```


<a href="#top">Back to top</a>

### Model diagnostics

Cross-sectional dependence test




```{r}
pcdtest(turnout ~ nightlight_mean +n.deaths_DRC_milit + n.deaths_foreign_milit +  n.deaths_non_state + n.deaths_civilians + n.deaths_unknow,data=to.model,model = "within",effect="twoways",w=nb.matrix)
```

Cross-sectional dependence

```{r}

plm::pwartest(turnout ~ nightlight_mean +n.deaths_DRC_milit + n.deaths_foreign_milit +  n.deaths_non_state + n.deaths_civilians + n.deaths_unknow,data=to.model)

```

Fixed effects test

```{r}
mpool <- plm::plm(turnout ~ nightlight_mean +n.deaths_DRC_milit + n.deaths_foreign_milit +  n.deaths_non_state + n.deaths_civilians + n.deaths_unknow,data=to.model,model="pooling")

plm::pFtest(m,mpool)

```


Residuals Normality

```{r}
resid <- residuals(m)

qqnorm(resid)
qqline(resid)

```

```{r}

ks.test(resid,"pnorm",mean(resid),sd(resid))

```

```{r}
pred <- predict(m)

plot(as.vector(pred),as.vector(resid),ylab="Residuals",xlab="Fitted")
```

<a href="#top">Back to top</a>

## 2.8 Models table

```{r,results='asis'}

models.to.print <- list(model1_1,model1_2,model1_3,model1_4,model1_5,model1_6,model1_7)

model_names <- c("Total Deaths","Log Total Deaths","Deaths by type","Total Conflicts","Log Total Conflicts","Conflicts by type","Conflict Deaths by side")

models.to.print_se <- map(models.to.print,~coeftest(.x, vcovHC(.x, method="arellano", type="HC3"))[,"Std. Error"])

out.file <- here::here("tables/turnout.vs.conflicts_and_nightlights_models.html")

 F.stat <-map(models.to.print,~{
  summ <- summary(.x,vcov.=vcovHC(.x, method="arellano", type="HC3"))
  
  .p <- summ$fstatistic$p.value
  sprintf("%0.3f%s",summ$fstatistic$statistic,
  case_when(.p<0.01 ~"***",
            .p<0.05 ~"**",
            .p<0.1~"*",
            TRUE ~""))
  
  
})  %>% unlist %>% c("F Statistic",.)

  df <-map(models.to.print,~{
  summ <- summary(.x,vcov.=vcovHC(.x, method="arellano", type="HC3"))
  
  paste(summ$fstatistic$parameter,collapse=";")
  
  
})  %>% unlist %>% c("df",.)
 

suppressWarnings(stargazer::stargazer(models.to.print,type="html",
                                      se=models.to.print_se,
                                      out =out.file ,
                                      column.labels=model_names,dep.var.caption = "Votes turnout",
                                      omit.stat = "f",
                                      add.lines = list(F.stat,
                                                       df)))

```

<a href="#top">Back to top</a>